Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-04-06 paper/articleNmfTrafficSimScene2018.tex
minor improvement

The evaluation corpus must be both realistic and non ambiguous in terms of traffic sound level. The former calls for the use of real urban sound environments, and the latter imposes the use of controlled sound sources with known properties: onset and offset time location, and sound level. Indeed, the precise annotation of the sound level of a given source of interest in a real recording is a very complex problem. Two corpora are proposed to design a valid corpus of  evaluation. The first, called the reference corpus, is a set of recordings of urban sound environments, from which, what we call, a transcription is made, \textit{i.e.} which sound source is present from this time to this time. The second, called the elemental corpus, is a set of monophonic recordings of isolated sound sources that represent categories of events that are present in the reference scenes. The elemental corpus is built with still existing sounds and with specific recordings, see part \ref{part:simScene}. The evaluation corpus is then designed by replicating the reference corpus according to the transcription with the help of the elemental corpus, see Figure \ref{fig:transcription}.
More precisely, the reference corpus is composed of 76 recordings from 2 to 5 min, achieved in the \nth{13} district of Paris (France) at 19 different locations \footnote{Recordings were made as part of the Grafic project funded by Ademe}, see Figure \ref{fig:map_grafic}, which cover various sound environments. A complete description of the experimental protocol can be found in \cite{aumond_modelling_2017}. Two of the 76 recordings are rejected for the analysis because the audio files were corrupted, resulting in 74 valid audio files assumed as representative of the variety of urban sound environments. The recordings are listened and categorized within four different sound environments, as proposed in \cite{can_describing_2015}: \textit{park} (8 audio files with a cumulative duration of 16min01), \textit{quiet street} (35 audio files with a cumulative duration of 77min27), \textit{noisy street} (23 audio files with a cumulative duration of 56min10) and \textit{very noisy street} (8 audio files with a cumulative duration of 21min42). Then, each audio file is transcripted, noticing the start, end time and level of each sound event along with its sound class. This annotation phase makes it possible to produce simulated sound scenes with the same positions of sound events than the recordings and therefore as close as possible to the real scenes.

@@

To evaluate the level of realism of the corpus of transcribed urban sound scenes, a perceptual test is considered.

The perceptual test is conducted with a panel of 50 subjects that are asked to assess the level of realism on a 7-point scale (1 is \textit{not realistic at all}, 7 is \textit{very realistic}) of a set of transcribed and recorded scenes. The total number of sound scenes tested is set at 40. This is less than the number of scenes available to ensure that each audio sample is sufficiently assess. The first half includes 20 30-seconds audio files corresponding to the real scenes, including 5 scenes that belong to the sound environment \textit{park}, 6 from \textit{quiet street}, 4 from \textit{noisy street} and 5 from \textit{very noisy street} chosen randomly among the recorded scenes. The second half is composed of the replicated scenes from the evaluation corpus corresponding to the same 20 reference scenes. In order to limit the duration of the test to preserve the concentration of the subjects, each subject listens to only a subset of 20 sound scenes. All the scenes are normalized to the same sound level, chosen at 65 dB, and the subjects are not allowed to change the output sound level once set at the beginning of the experiment.

@@

The test was available online from February 8th, 2017 and the needed number of participant (50) has been reached 12 days later. During the test, the participants had the possibility to listen to each scene as many times as wanted before assessing, without being able to change their judgment afterwards. The participants could also leave a comment on each audio to explain the rating \footnote{The interface of the experiment is available \url{http://soundthings.org/research/xpRealism}}. Based on the information provided, the panel of 50 listeners was made of 31 males and 18 females (one not documented) with an average age of 36 ($\pm$ 12) years old. $62\%$ of the participants declared having no experience in the listening of urban sound mixtures. 
The results show that the average score (with its standard deviation) of all the replicated scenes ($m_{replicated}$ = 5.1 ($\pm$ 1.6)) is close to the recorded ones ($m_{recorded}$ = 4.9 ($\pm$ 1.6)).

To determine whether a replicated scene is perceived in a similar way to that recorded, a Student's t-test is performed, for each scene, between the scores from the recorded sample and those from the replicated sample with the $H_0$ hypothesis which considers the similarity between the distribution of the rates for the recorded and the replicated scenes of each participant with a \textit{p-value} threshold of 5$\%$.  The 20 performed t-tests show that the differences in the assessment of the replicated and the recorded scene, according to their degree or realism, is not significant (p-value$>5\%$).

>>>>

The evaluation corpus must be both realistic and non ambiguous in terms of traffic sound level. The former calls for the use of real urban sound environments, and the latter imposes the use of controlled sound sources with known properties: onset and offset time location, and sound level. Indeed, the precise annotation of the sound level of a given source of interest in a real recording is a very complex problem. Two corpora are proposed to design a valid corpus of  evaluation. The first, called the reference corpus, is a set of recordings of urban sound environments, from which, what we call, a transcription is made, \textit{i.e.} which sound source is present from this time to this time. The second, called the elemental corpus, is a set of monophonic recordings of isolated sound sources that represent categories of events that are present in the reference scenes. The elemental corpus is built with still existing sounds and with specific recordings, see part \ref{part:simScene}. The evaluation corpus is then designed by replicating the reference corpus according to the transcription with the help of the elemental corpus, see Figure \ref{fig:transcription}.

The reference corpus is composed of 76 recordings from 2 to 5 min, achieved in the \nth{13} district of Paris (France) at 19 different locations \footnote{Recordings were made as part of the Grafic project funded by Ademe}, see Figure \ref{fig:map_grafic}, which cover various sound environments. A complete description of the experimental protocol can be found in \cite{aumond_modelling_2017}. Two of the 76 recordings are rejected for the analysis because the audio files were corrupted, resulting in 74 valid audio files assumed as representative of the variety of urban sound environments. The recordings are listened and categorized within four different sound environments, as proposed in \cite{can_describing_2015}: \textit{park} (8 audio files with a cumulative duration of 16min01), \textit{quiet street} (35 audio files with a cumulative duration of 77min27), \textit{noisy street} (23 audio files with a cumulative duration of 56min10) and \textit{very noisy street} (8 audio files with a cumulative duration of 21min42). Then, each audio file is transcripted, noticing the start, end time and level of each sound event along with its sound class. This annotation phase makes it possible to produce simulated sound scenes with the same positions of sound events than the recordings and therefore as close as possible to the real scenes.

@@

To evaluate the level of realism of the evaluation corpus composed of replicated urban sound scenes, a perceptual test is considered.

The perceptual test is conducted with a panel of 50 subjects that are asked to assess the level of realism on a 7-point scale (1 is \textit{not realistic at all}, 7 is \textit{very realistic}) of a set of replicated and recorded scenes. The total number of sound scenes tested is set at 40. This is less than the number of scenes available to ensure that each audio sample is sufficiently assess. The first half includes 20 30-seconds audio files corresponding to the real scenes, including 5 scenes that belong to the sound environment \textit{park}, 6 from \textit{quiet street}, 4 from \textit{noisy street} and 5 from \textit{very noisy street} chosen randomly among the recorded scenes. The second half is composed of the replicated scenes from the evaluation corpus corresponding to the same 20 reference scenes. In order to limit the duration of the test to preserve the concentration of the subjects, each subject listens to only a subset of 20 sound scenes. All the scenes are normalized to the same sound level, chosen at 65 dB, and the subjects are not allowed to change the output sound level once set at the beginning of the experiment.

@@

The test was available online from February 8th, 2017 and the needed number of participant (50) has been reached 12 days later. During the test, the participants had the possibility to listen to each scene as many times as wanted before assessing, without being able to change their judgment afterwards. The participants could also leave a comment on each audio to explain the rating \footnote{The interface of the experiment is available \url{http://soundthings.org/research/xpRealism}}. Based on the information provided, the panel of 50 listeners was made of 31 males and 18 females (one not documented) with an average age of 36 ($\pm$ 12) years old. $62\%$ of the participants declared having no experience in the listening of urban sound mixtures. 
The results show that the average score (with its standard deviation) of all the replicated scenes ($m_{replicated}$ = 5.1 ($\pm$ 1.6)) is close to the recorded ones ($m_{recorded}$ = 4.9 ($\pm$ 1.6)). To determine whether a replicated scene is perceived in a similar way to that recorded, a Student's t-test is performed, for each scene, between the scores from the recorded sample and those from the replicated sample with the $H_0$ hypothesis which considers the similarity between the distribution of the rates for the recorded and the replicated scenes of each participant with a \textit{p-value} threshold of 5$\%$.  The 20 performed t-tests show that the differences in the assessment of the replicated and the recorded scene, according to their degree or realism, is not significant (p-value$>5\%$).
